Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-27 review_article.Rmd
rearrangement of sections
allow changes to be made to the figures

# Disease mapping methods

## Current best practice map displays for cancer data

@@

```{r choropleth-grid-create, message=FALSE, eval = FALSE}
library(grid)
library(png)
library(gridExtra)

@@

## Publicly available atlases using choropleth methods

@@

## Cartograms as an alternative display

@@

### Alternative Displays

@@

# A discussion of mapping methods

>>>>

# Map displays for disease data

@@

```{r choropleth-grid-create, message=FALSE}
library(grid)
library(png)
library(gridExtra)

@@

# Publicly available atlases

@@

# Alternative displays

## Cartograms

@@

### Alternatives

@@

# Comparison of mapping methods
